---
title: "R Notebook"
output: html_notebook
---


# Load and filter the data

```{r}

library(tidyverse)

rna_df <- read_tsv("rna_tissue_wide.tsv", na="0") %>% data.frame()

rna_sdf <- rna_df[, -c(1,2,3)]
rownames(rna_sdf) <- rna_df$Gene
head(rna_sdf)

non_na_thres <- 10
row_na_counts <- rowSums(is.na(rna_sdf))

row_na_counts

rna_sdf_filter <- rna_sdf[row_na_counts < non_na_thres, ]
message("Before filter: ", nrow(rna_sdf), " after filter: ", nrow(rna_sdf_filter))

```


# Calculate correlations and network

```{r}
# corr_mat <- cor(t(rna_sdf), method="spearman")

library(Hmisc)
mycor <- rcorr(t(head(rna_sdf, 20)), type="spearman")
mycor$P

library(reshape2)
long_df <- melt(mycor$P)
long_df_filter <- long_df %>% filter(value < 0.0000001)
```

# Try reading into network

```{r}
long_df <- read_tsv("p_long_p0000001.tsv.gz")
head(long_df)

library(igraph)

nrow(long_df)

use_count <- 2000000
graph_from_data_frame(head(long_df, use_count))
```

# Calculating out-degree correlation

1. Load transcript correlation matrix
2. Load protein interaction matrix
3. Perform out-degree calculations
4. Extract out-degree vectors linked to gene IDs
5. Extract common gene IDs
6. Calculate the correlation

Packages

```{r}
library(igraph)
library(tidyverse)
library(gridExtra)
```

Load data

```{r}
trans_corr <- read_tsv("p_long_p0001.tsv.gz")
# trans_corr <- read_tsv("p_long_p0000001.tsv.gz")
prot_int <- read_tsv("ppi_human_stringdb_ensp2ensg2.tab.gz")
use_count <- Inf

message("Transcript entries: ", nrow(trans_corr))
message("Prot entries: ", nrow(prot_int))

message("Transcripts per prot: ", nrow(trans_corr) / nrow(prot_int))
```

Generate graphs

```{r}
thresholds <- c(1e-3, 1e-4, 1e-5)
# thresholds <- c(1e-3, 1e-4, 1e-5, 1e-6, 1e-7, 1e-8, 1e-9, 1e-10, 1e-11, 1e-12)

prot_graph <- graph_from_data_frame(head(prot_int[, c("gene1", "gene2")], use_count))
prot_deg <- igraph::degree(prot_graph, mode="out")

plts <- list()
corrs <- list()

for (i in seq_len(length(thresholds))) {
    thres <- thresholds[i]
    message("Processing threshold: ", thres)
    
    subset_trans <- trans_corr %>% filter(value < thres)
    trans_graph <- graph_from_data_frame(head(trans_corr, use_count))
    trans_deg <- igraph::degree(trans_graph, mode="out")
    common_names <- intersect(names(trans_deg), names(prot_deg))
    common_trans_out <- trans_deg[common_names]
    common_prot_out <- prot_deg[common_names]
    out_deg_df <- data.frame(
        trans=common_trans_out,
        prot=common_prot_out
    )
    
    plts[[i]] <- grid.arrange(
        ggplot(out_deg_df, aes(x=trans)) + geom_histogram(bins=100) + theme_classic() + xlim(NA, 2000),
        ggplot(out_deg_df, aes(x=prot)) + geom_histogram(bins=100) + theme_classic() + xlim(NA, 2000)
    )

    message(cor(out_deg_df$trans, out_deg_df$prot, method="pearson"))
    message(cor(out_deg_df$trans, out_deg_df$prot, method="spearman"))
    
    message(cor.test(out_deg_df$trans, out_deg_df$prot, method="pearson"))
    message(cor.test(out_deg_df$trans, out_deg_df$prot, method="spearman"))
    
}





head(trans_deg)
head(prot_deg)

```

Next steps: Calculating correlation of out degree

(Possibly also do some differential thresholding?)

```{r}
```























